---
title: "Exploring the BRFSS data"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Setup

### Load packages

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
```

### Load data

Make sure your data and R Markdown files are in the same directory. When loaded
your data file will be called `brfss2013`. Delete this note when before you submit 
your work. 

```{r load-data}
#load("brfss2013.RData")
```

* * *

## Part 1: Data

#### Collection

The BRFSS data is collected via telephone interviews
of noninstitutionalized adults (those who are not prisoners or long-term patients) who 
are 18 years old or older and live in the United States.

These interviews are conducted by health departments in each state using in-house 
interviewers, contracted telephone call centers, or universities.

The phone numbers are obtained using a random digit dialing (RDD) technique 
for both landlines and cell phones.

#### Causality

Because this data is not collected using a controlled experiment, 
no causation of changes in the values of any variables can be determined.

#### Generalizability

Based on the fact that the 2013 American Community Survey (ACS)
reported that 97.7% of all households in the U.S. have some form of telephone service,
the method of acquiring phone numbers was a random dialing system,
and the sample size was large at 491,775 observations,
it could be argued that the sample statistics are generalizable to the the entire U.S. adult population.

However, the willingness, or lack thereof, to participate in the survey could
signal a significant difference between the disposition or lifestyle of those 
who participated and those who declined to do so.


* * *

## Part 2: Research questions

**Research quesion 1:**


What time is it?





**Research quesion 2:**


What is your favorite food?





**Research quesion 3:**





* * *

## Part 3: Exploratory data analysis

NOTE: Insert code chunks as needed by clicking on the "Insert a new code chunk" 
button (green button with orange arrow) above. Make sure that your code is visible
in the project you submit. Delete this note when before you submit your work.

**Research quesion 1:**

```{r}

```



**Research quesion 2:**

```{r}

```



**Research quesion 3:**

```{r}

```

